Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks

### 2020-03-13 paper/paper.tex
draw dome

	\section{ABSTRACT}\label{sec:abstract}
	Deep learning methods have shown their marvel performance on hyper-spectral image (HSI) classification tasks.
	In particular,algorithms based on Convolution Neural Network (CNN) outperforms most of the conventional machine-
	learning based algorithms.
	Recently, a newly proposed neural network called Capsule Network (CapsNet) showed its potential to replace the CNNs
	in various classification tasks with its amazing performance.
	In this paper, we proposed a new network architecture based on CapsNet for HSI classification tasks, called
	Dual-channel Capsule Network (DCCN).
	Our DCCN model extracts features from spectral and spatial domain respectively with two separate convolution
	channels and then concatenates and feds the features into the capsule layer to classify each of the HSI pixels.
	The model is trained and tested on \textbf{(2/3/4/5?)} real HSI dataset \textbf{(Pavia University, Pavia City,
	Salinas Valley, Salinas A and KSC)} and achieved high accuracy.
	We also compared our network with some of the state-of-art models and found our model outperformed these models.
	Among these state-of-art models we also implemented the Capsule Network that has the same architecture as our
	network except the spectral convolution channel, and we found the DCCN model was superior to it as well.

@@

	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
	dataset, which is a small subset of the Salinas Valley dataset.
	The first three of them are relatively large dataset and the last one is relatively small.
	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
	Here follows the brief introduction of the four dataset(see table\ref{psgt}).
	\begin{enumerate}[1)]
		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
		campaign over Pavia, northern Italy.
		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
		Pavia Centre is a 1096×1096 pixels image, and Pavia University is 610×610 pixels, but some of the samples in
		both images contain no information and have to be discarded before the analysis, so the final picture size is
		1096×715 and 610×340.
		The geometric resolution is 1.3 meters.
		Both image has 9 different ground truth classes each.
		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
		California, and is characterized by high spatial resolution (3.7-meter pixels).
		The Salinas Valley dataset is a 512×217 pixels image, and the Salinas A is a subset of the Salinas Valley
		containing 86×83 pixels.
		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
		bands left in both of the tow dataset.
		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes.
	\end{enumerate}
	\begin{table}[h]
		\centering
		\tiny
		\resizebox{\textwidth}{!}{
			\begin{tabular}{|c|c|c|c|}

@@

			\end{tabular}}
		\caption{Number of samples in two Pavia scene dataset.}
		\label{psgt}
	\end{table}

@@

	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
	SVM,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{liu2017semi},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	CapsNet and DCCN together in table~\ref{result}.
	From the results reported in table~\ref{result}, we can observe that our proposed DCCN model outperforms all the
	other seven state-of-art models on all 4 dataset.
	Among all competitors in this experiment, 3D CNN\cite{hamida20183} and the CapsNet model performed relatively second
	best, since both of the two model achieved second high accuracy on different dataset.
	This is expected because both of the two algorithm are spectral-spatial based so they can utilize more information,
	compared to the 2D CNN, FCN, SVM and CNN-MRF classifiers, to classify the HSI pixels.
	Nevertheless, our DCCN model can consistently outperform the second-best algorithm with an average \textbf{fill data
	here} for AA, OA, $\kappa$.

	\begin{table}[htb]
		\tiny
		\centering
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			 &\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
			\hline
			\begin{tabular}{c}
				\textbf{model}\\
				\hline
				{SVM}\\
				{1D CNN\cite{hu2015deep}}\\
				{2D CNN\cite{liu2017semi}}\\
				{3D CNN\cite{hamida20183}}\\
				{3D FCN\cite{lee2016contextual}}\\
				{CNN-MRF\cite{cao2018hyperspectral}}\\
				{CapsNet}\\
				{DCCN}\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}\\
			\hline
		\end{tabular}
		\caption{Final result of all adopted models.}
		\label{result}
	\end{table}

	In figure~\ref{pupm,pcpm,svpm,sapm} we presented the classification maps outputted by our DCCN and seven competitor

@@

@@

@@

@@

@@

	figure~\ref{pcpd ,pupd,svpd,sapd}.

@@

>>>>

	\section{ABSTRACT}\label{sec:abstract}
	Deep learning methods have shown their marvel performance on hyper-spectral image (HSI) classification tasks.
	In particular,algorithms based on Convolution Neural Network (CNN) outperforms most of the conventional machine-
	learning based algorithms.
	Recently, a newly proposed neural network called Capsule Network (CapsNet) showed its potential to replace the CNNs
	in various classification tasks with its amazing performance.
	In this paper, we proposed a new network architecture based on CapsNet for HSI classification tasks, called
	Dual-channel Capsule Network (DCCN).
	Our DCCN model extracts features from spectral and spatial domain respectively with two separate convolution
	channels and then concatenates and feds the features into the capsule layer to classify each of the HSI pixels.
	The model is trained and tested on four real HSI dataset, i.e., Pavia University, Pavia City,
	Salinas Valley and Salinas A, and achieved high accuracy.
	Moreover, our DCCN model has much higher confident for the predicted accuracy compared to the competitor algorithms.
	We also compared our network with some of the state-of-the-art models and found our model outperformed these models.
	Among these state-of-the-art models we also implemented the Capsule Network that has the same architecture as our
	network except the spectral convolution channel, and we found the DCCN model was superior to it as well.

@@

	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
	\begin{table}[h]
		\centering
		\tiny
		\resizebox{\textwidth}{!}{
			\begin{tabular}{|c|c|c|c|}

@@

			\end{tabular}}
		\caption{Number of samples in two Pavia scene dataset.}
		\label{psgt}
	\end{table}
	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
	dataset, which is a small subset of the Salinas Valley dataset.
	The first three of them are relatively large dataset and the last one is relatively small.
	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
	Here follows the brief introduction of the four dataset(see table\ref{psgt}).
	\begin{enumerate}[1)]
		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
		campaign over Pavia, northern Italy.
		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
		Pavia Centre is a 1096×1096 pixels image, and Pavia University is 610×610 pixels, but some of the samples in
		both images contain no information and have to be discarded before the analysis, so the final picture size is
		1096×715 and 610×340.
		The geometric resolution is 1.3 meters.
		Both image has 9 different ground truth classes each.
		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
		California, and is characterized by high spatial resolution (3.7-meter pixels).
		The Salinas Valley dataset is a 512×217 pixels image, and the Salinas A is a subset of the Salinas Valley
		containing 86×83 pixels.
		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
		bands left in both of the tow dataset.
		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes.
	\end{enumerate}

@@

	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
	SVM,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{liu2017semi},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	CapsNet and DCCN together in table~\ref{result}.
	From the results reported in table~\ref{result}, we can observe that our proposed DCCN model outperforms all the
	other seven state-of-the-art models on all 4 dataset.
	Among all competitors in this experiment, 3D CNN\cite{hamida20183} and the CapsNet model performed relatively second
	best, since both of the two model achieved second high accuracy on different dataset.
	This is expected because both of the two algorithm are spectral-spatial based so they can utilize more information,
	compared to the 2D CNN, FCN, SVM and CNN-MRF classifiers, to classify the HSI pixels.
	Nevertheless, our DCCN model can consistently outperform the second-best algorithm with an average \textbf{fill data
	here} for AA, OA, $\kappa$.

	\begin{table}[htb]
		\tiny
		\centering
		\resizebox{\textwidth}{!}{
			\begin{tabular}{|c|c|c|c|c|}
				\hline
				&\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
				\hline
				\begin{tabular}{c}
					\textbf{metrics}\\
					\hline
					{SVM}\\
					{2D CNN\cite{liu2017semi}}\\
					{3D CNN\cite{hamida20183}}\\
					{3D CNN-MS\cite{he2017multi}}\\
					{3D FCN\cite{lee2016contextual}}\\
					{CNN-MRF\cite{cao2018hyperspectral}}\\
					{CapsNet}\\
					{DCCN}
				\end{tabular}&
				\begin{tabular}{ccc}
					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
					\hline
					97.52±0.07 & 91.74±0.33 & 96.49±0.10\\
					98.27±0.14 & 97.24±0.54 & 97.56±0.19\\
					95.25±2.99 & 89.74±7.37 & 93.32±4.21\\
					98.03±0.40 & 96.31±1.42 & 97.22±0.56\\
					98.33±0.59 & 94.65±2.09 & 97.64±0.83\\
					99.24±0.23 & 97.54±1.04 & 98.92±0.33\\
					99.48±0.09 & 98.50±0.21 & 99.27±0.12\\
					\textbf{99.53±0.02} & \textbf{98.59±0.20} & \textbf{99.34±0.03}
				\end{tabular}&
				\begin{tabular}{ccc}
					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
					\hline
					79.86±0.26 & 64.26±0.45 & 71.86±0.39\\
					93.74±0.42 & 95.61±0.79 & 91.85±0.54\\
					77.92±12.22 & 85.34±7.42 & 73.42±13.63\\
					93.39±1.34 & 95.97±1.39 & 91.42±1.72\\
					88.45±1.66 & 85.58±3.22 & 84.49±2.22\\
					98.07±0.62 & 96.80±1.06 & 97.44±0.82\\
					97.69±0.60 & 96.82±0.83 & 96.94±0.80\\
					\textbf{98.40±0.19} & \textbf{97.77±0.33} & \textbf{97.89±0.25}
				\end{tabular}&
				\begin{tabular}{ccc}
					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
					\hline
					82.45±0.75 & 86.16±0.93 & 80.24±0.87\\
					92.24±1.19 & 95.82±0.61 & 91.36±1.34\\
					88.27±4.18 & 92.76±2.96 & 86.87±4.74\\
					91.29±2.91 & 95.08±1.68 & 90.28±3.27\\
					87.11±3.77 & 90.10±3.66 & 85.57±4.28\\
					94.69±1.48 & 97.39±0.80 & 94.07±1.66\\
					94.48±0.59 & 96.84±0.58 & 93.83±0.66\\
					\textbf{95.00±0.59} & \textbf{97.30±0.50} & \textbf{94.42±0.66}
				\end{tabular}&
				\begin{tabular}{ccc}
					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
					\hline
					97.44±0.19 & 97.42±0.22 & 96.80±0.23\\
					84.47±0.51 & 89.86±0.69 & 81.22±0.62\\
					79.27±4.74 & 80.81±8.80 & 74.70±5.96\\
					79.92±4.91 & 85.46±5.01 & 75.99±5.69\\
					86.54±3.72 & 85.55±4.30 & 83.09±4.65\\
					98.00±1.61 & 97.10±2.33 & 97.48±2.03\\
					99.52±0.10 & 99.31±0.15 & 99.40±0.13\\
					\textbf{99.56±0.05} & \textbf{99.36±0.07} & \textbf{99.45±0.06}
				\end{tabular}\\
				\hline
			\end{tabular}
		}
		\caption{AA, OA and Kappa metrics for all 8 algorithms.
		We can observe that out proposed model outperformed all competitor algorithms for all 4 dataset.}
		\label{result}
	\end{table}

	In figure~\ref{pupm},\ref{pcpm},\ref{svpm},\ref{sapm} we presented the classification maps outputted by our DCCN and seven competitor

@@

		\caption{Predicted map for all 8 algorithms on the Pavia Center dataset.}

@@

		\caption{Predicted map for all 8 algorithms on the Pavia University dataset.}

@@

		\caption{Predicted map for all 8 algorithms on the Salinas Valley dataset.}

@@

		\caption{Predicted map for all 8 algorithms on the Salinas A dataset.}

@@

	figure~\ref{pcpd} ,\ref{pupd},\ref{svpd},\ref{sapd}.

@@

		\caption{Probability map for all 8 algorithms on the Pavia City dataset.}
